Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-30 paper-filmat.tex
Make intended readership more clear (in response to review)

We intend this contribution to be self-contained and do not assume familiarity with
topos theory or category theory. Readers who would like to learn more details
are directed to the survey of category theory by Jean-Pierre
Marquis~\cite{sep:category-theory} and to a gentle introduction to topos theory
by Tom Leinster~\cite{leinster:introduction}. Standard references for the internal
language of toposes include~\cite[Chapter~VI]{moerdijk-maclane:sheaves-logic},
\cite[Chapter~14]{goldblatt:topoi},
\cite{caramello:preliminaries}, \cite{streicher:ctcl}, \cite{shulman:categorical-logic},
\cite[Chapter~6]{borceux:handbook3} and~\cite[Part~D]{johnstone:elephant}.

>>>>

We intend this contribution to be self-contained and do not assume familiarity with
topos theory or category theory, having a diverse readership of philosophers of
mathematics in mind. However, to make this text more substantial to
categorically-inclined readers, some categorical definitions are included.
These definitions can be skipped without impacting the main message of this contribution.

Readers who would like to learn more details
are directed to the survey of category theory by Jean-Pierre
Marquis~\cite{sep:category-theory} and to a gentle introduction to topos theory
by Tom Leinster~\cite{leinster:introduction}. Standard references for the internal
language of toposes include~\cite[Chapter~VI]{moerdijk-maclane:sheaves-logic},
\cite[Chapter~14]{goldblatt:topoi},
\cite{caramello:preliminaries}, \cite{streicher:ctcl}, \cite{shulman:categorical-logic},
\cite[Chapter~6]{borceux:handbook3} and~\cite[Part~D]{johnstone:elephant}.
